



\documentclass[12pt]{report}

% for navigation within the generated pdf
\usepackage{hyperref}
% for abbreviations
\usepackage{acro}
% for code snippets
\usepackage{listings}
% to frame code listings nicely in a box
\usepackage{framed}
% for color utilities
\usepackage{xcolor}
% for figs
\usepackage{graphicx}
% for new fonts
\usepackage{courier}
% avoid showing "Chapter" text
\usepackage{titlesec}


\DeclareAcronym{sihft}{
  short=SIHFT,
  long=Software Implemented Hardware Fault Tolerance,
}

% make sure no indentation done for new paragraphs
\setlength\parindent{0pt}


% title content
\date{\today}
\title{
\textbf{COMPAS-FT-RISCV} \\
\large Compiler Assisted Fault Tolerance for RISCV Architectures \\
\small Version 1.0.0
}
\author{
ESL Group, Chair of Electronic Design Automation \\
Department of Electrical and Computer Engineering \\
Technical University of Munich
}

% avoid showing meaningless "Chapter" for manual content
\titleformat{\chapter}[display]
  {\normalfont\huge\bfseries}{}{0pt}{\Huge}
\titlespacing*{\chapter}
  {0pt}{10pt}{40pt}

% disable hyperref colors on links in generated pdf
% \hypersetup{
%   colorlinks=true, linkcolor=black, anchorcolor=black, citecolor=black,
%   filecolor=black, menucolor=black, runcolor=black, urlcolor=black]
% }
\hypersetup{
  colorlinks=true, linkcolor=black, anchorcolor=black, citecolor=black,
  filecolor=black, menucolor=black, runcolor=black, urlcolor=black
}

\begin{document}

\maketitle

\tableofcontents
\listoffigures

\newpage
\printacronyms

\chapter{User Manual}

\section{Overview}
COMPAS-FT-RISCV compiler was developed as part of the research work conducted in SAFE4I project. SAFE4I is funded by
the BMBF Ministry (Germany's Federal Ministry of Education and Research) under project grant 01IS17032. The authors
are responsible for the content of this document. \\

Compiler transformations to build soft error resilience into embedded software are highly attractive owing to their
superior error detection as well as automation properties. Before starting this work, we experienced a tooling
gap with in the RISC-V eco-system for ensuring functional safety for embedded firmware. This work aims to fill this gap
by providing a library of LLVM passes (C++ modules) that can be integrated in a modern LLVM codebase.
The resulting compiler is then able to provide various state-of-the-art
\textit{Software Implemented Hardware Fault Tolerance} (\ac{sihft}) transformations on a given C/C++ project. \\

Specifically, we have implemented the following \ac{sihft} methods:
\begin{itemize}
 \item{EDDI \cite{eddi} for data-flow protection}
 \item{SWIFT \cite{swift} for data-flow protection}
 \item{NZDC \cite{nzdc} for data-flow protection}
 \item{NEMESIS \cite{nemesis} for conditional branch protection}
 \item{CFCSS \cite{cfcss} for control flow protection}
 \item{RASM \cite{rasm} for control flow protection}
 \item{REPAIR \cite{repair} for combined data-flow and control-flow protection}
\end{itemize}

This document serves to be the user manual for the developed compiler. We now provide instructions on how to setup the
LLVM compiler in order to use the implemented \ac{sihft} transformations.

% installation guide section
\newpage
\input{installation_guide}

% user guide section
\newpage
\input{user_guide}

% references
\bibliographystyle{apalike}
\bibliography{references}


\end{document}
